Zero-Knowledge Credentials for Smart Contracts

### 2018-05-13 paper/paper.tex
Added details about ZKID Web3 Framework

The properly interface with the ZKID Service a dApp will have to provide an annotated ABI for its dependant contract(s).
The required annotations describe the required credentials for a given method within the smart contract and will
be used to propery construct public inputs and subsequently generate proofs for credentials. An annotated ABI function
would appear as follow:

\begin{lstlisting}

  {"constant":false,
   "name":"Join",
   "inputs":[],
   "outputs":[],
   "payable":false,
   "type":"function","
    "credentials":[
      {"contract_salt":"0xdeadbeef",
      "high_bound":150,
      "low_bound":18,
      "k_factor":1,
      "description": "Confirms holder is over 18."
      }
    ]

Additionally, all credential-enabled contracts are required to implement a GetMerkleTreeAddress function that can provide
the caller with the IPFS address of its merkle root. This is pertinent to the generation of the nessesary Merkle Tree membership
proofs and proof generation will be unsuccessful if ignored.

\subsection{ZKID Service}

@@

\subsubsection{JSON RPC Service}

The ZKID client application acts as a JSON RPC service that can handle requests from client dApps. For the simplest implementation,
the RPC service offered a single procedure: GenerateProofs. This procedure takes as input all the fields nessesary
to construct the required set of public inputs for the proofs. If proof generation was successful, the service will respond with a 
set of generated proofs as well as their relative public inputs. The returned proofs can then be sent to the verifier contract.

@@

It is expected, although not required, that credential-enabled contracts perform their own verification. For this reason, we have
provided a Solidity library enables contracts to verify proofs autonomously. The verifier library follows a scheme similar to that
of Zokrates [insert citation here]. The library exposes a single method to be utlized by the higher-level contract: verifyTx. This 
method does precisely what the name implies and verifies as set of proofs encoded as bytes and returns true if all proofs where sucessfully
verified and false otherwise.

@@

Although there is no strict template for an issuer (asside from the credential contruction), we purpose a scheme that we believe
will offers most of the elementary functions of an issuer.

@@

>>>>

\subsection{Credential Scheme}

\subsection{The ZKID Service}

@@

\subsubsection{JSON RPC}

The ZKID client application acts as a JSON RPC service that can handle requests from client dApps. For the simplest implementation,
the RPC service offered a single procedure: GenerateProofs. This procedure takes as input all the fields nessesary
to construct the required set of public inputs for the proofs. If proof generation was successful, the service will respond with a 
set of generated proofs and relevant public inputs. The returned proofs can then be sent to the verifier contract.

@@

It is expected, although not required, that credential-enabled contracts perform their own proof verification. For this reason, we have
developed a Solidity library that enables contracts to verify proofs autonomously. The verifier library follows a scheme similar to that
of Zokrates [insert citation here]. The library exposes a single method to be utlized by the higher-level contract: verifyTx. This 
method does precisely what the name implies and verifies as set of proofs encoded as bytes and returns true if all proofs where sucessfully
verified and false otherwise.

@@

Although there is no strict template for an issuer (asside from the credential contruction), we purpose a scheme that we believe
will offers most of the elementary functions of an issuer. This basic scheme involves 2 main functions:
credential-holder stake and distributed merkle tree storage.

\subsubsection{Credential-Holder Stake}

An obvious vulenerability of the credential system as described is the ability to share credentials. So, for example, an uncredible could may
a credible party for a specific credential. We proprose that an issuer's require a credential-requester to submit a stake when 
applying for a credential. This stake can be redeemed by an user that can provide the issuer contract with a specified pre-image. Once 
redeemed, the credential because invalidated. Therefore, if a dishonest party were to give away their credential, the new holder of the credential
could steal the original holder's stake. This requires issuers to set their stakes high enough such that no party would be willing to pay the
price of the stake for the credential. A stake system could also lead to varying "tiers" of issuers where issuers that require higher stakes could be 
percieved as having higher credibility do the lower probability of users sharing said issuer's credential.

@@

Add some Introduction here

\subsubsection{Credential Annotated ABI}
The properly interface with the ZKID Service a dApp will have to provide an annotated ABI for its dependant contract(s).
The required annotations describe the required credentials for a given method within the smart contract and will
be used to propery construct public inputs and subsequently generate proofs for credentials. An annotated ABI function
would appear as follow:
\begin{lstlisting}

  {"constant":false,
   "name":"Join",
   "inputs":[],
   "outputs":[],
   "payable":false,
   "type":"function","
    "credentials":[
      {"contract_salt":"0xdeadbeef",
      "high_bound":255,
      "low_bound":18,
      "k_bound":1,
      "description": "Confirms holder is over 18."
      }
    ]
  }
\end{lstlisting}

\subsubsection{ZKID web3 Framework}

To a dApp's migration to credentail-enabled contracts as smooth as possible we have supplied a ZKID framework that interfaces
with our prove-generation service and seemlessly collects and supplies verifcation arguments to credential-enabled methods. This 
allows dApp creators to integrate credential functionality without changing their already developed application code.

To utlize the framework a dApp simply replaces all existing contract calls with calls to their credential accepting counterparts. 
This can be accomplished very concisely by wrapping the credial-accepting method call with partially applied
function. A full implementation of this exists in our example application and is depicted in [INSERT FIG NUMBER];
\begin{lstlisting}
function OnJoinClick() {
  var credBlock = new CredentialBlock("Join", PartialAppJoin(), lottery_abi);
    credBlock.display();
}

function PartialAppJoin(/* Insert non-proof arguments here*/) {
  return function (proof_bytes) {
    contractInstance.methods["Join"](/* Non-Proof Arguments*/ ,proof_bytes).send();
  }
}

In the above example, "Join" allowed a users to join a lottery if they have the required credentials. Originally, took a number of non-proof arguments. 
The credential enabled join now takes the non-proof arguments as well as proof arguments. This partial application hides the non-proof arguments from the ZKID CredentialBlock and allows the CredentialBlock to 
supply the proof arguments post proof-generation. The dApp's code has now migrated its call to "Join" to a credential-enabled call with minimal additions.
